Unrecognized States: A Theory of Self-Determination and Foreign Influence

### 2015-11-19 draft.tex
clarify outcomes vs. eq'a in alternative outcomes section

In the equilibrium under consideration here, the patron will invest to maintain an outcome that is not its most preferred, but it will not invest to achieve its most preferred outcome. This behavior may appear counterintuitive, but we frequently observe patron states whose preferred outcomes are recognized independence for the secessionists who  nonetheless contribute resources to sustain a status-quo outcome that is costly to all involved. The patron does not attempt to contribute sufficient resources to force recognition by the home state because doing so would induce offsetting expenditures by the international community to prevent this outcome.\footnote{We do not provide conditions on the budget of player $c$ similar to Restrictions (5) and (6): since the size of the international community relative to any particular country is large, it can be assumed that a budget constraint does not bind.}

@@

If the payoffs from Fight are strictly greater than the payoffs from Cede for both players, then (Fight,Fight) will be the only additional equilibrium outcome. If this inequality holds for just one player, then we have only the additional outcome in which that player chooses Fight and its opponent cedes. If both players strictly prefer Cede to Fight, then both the (Fight, Cede) and (Cede,Fight) outcomes are added to the status quo outcome.\footnote{In the case of any indifference, we get the relevant combination of (Fight, Fight), (Fight,Cede) and (Cede, Fight).}

>>>>

In the Status Quo equilibrium, the patron will invest to maintain an outcome that is not its most preferred, but it will not invest to achieve its most preferred outcome. This behavior may appear counterintuitive, but we frequently observe patron states whose preferred outcomes are recognized independence for the secessionists who  nonetheless contribute resources to sustain a status-quo outcome that is costly to all involved. The patron does not attempt to contribute sufficient resources to force recognition by the home state because doing so would induce offsetting expenditures by the international community to prevent this outcome.\footnote{We do not provide conditions on the budget of player $c$ similar to Restrictions (5) and (6): since the size of the international community relative to any particular country is large, it can be assumed that a budget constraint does not bind.}

@@

If the payoffs from Fight are strictly greater than the payoffs from Cede for both players, then (Fight,Fight) will be the only additional equilibrium outcome. If this inequality holds for just one player, then we have only the additional outcome in which that player chooses Fight and its opponent cedes. If both players strictly prefer Cede to Fight, then there exist equilibria where both (Fight,Cede) and (Cede,Fight) are outcomes of the stage game.\footnote{In the case of any indifference, we get the relevant combination of (Fight, Fight), (Fight,Cede) and (Cede, Fight).}
